Equations & R Code

### 2017-02-23 manuscript/coexistence-stability_ms.Rmd
trivial writing

The opposing effects of environmental variability on ecosystem variability might explain the mixed results from \new{observational} studies on the diversity-\new{ecosystem variability} relationship.
Observational tests of the diversity-\new{ecosystem variability} relationship, which require sampling across natural diversity gradients, have yielded negative [@Hautier2014], neutral [@Valone2003; @Cusson2015], and positive [@Sasaki2011] relationships.
In a meta-analysis of diversity-\new{ecosystem variability} relationships @Jiang2009 found no significant evidence for an effect of species richness on ecosystem variability when restricting data to observational studies in terrestrial ecosystems, perhaps because environmental variability varies across natural diversity gradients, affecting both richness and ecosystem variability.
The idiosyncratic results of these observational studies contrast with the consistent conclusions from \new{experimental and theoretical work that ignore, or control, the} feedbacks between variability and richness.

@@

1. Does the diversity-variability relationship remain negative when species coexistence is maintained by the temporal storage effect or relative nonlinearity?

@@

\new{To bound the problem and to isolate the effect of fluctation-dependent coexistence on the diversity-ecosystem stability relationship we constrain our analysis to four species communities and do not consider communities where coexistence is maintained by a combination of mechanisms.
We limit our analysis to four species communities to keep the models tractable while still allowing enough of a species richness gradient for trends to emerge.
It is notoriously difficult to get more than four species to coexist via relative nonlinearity without introducing some form of fluctuation-independent mechanism like resource partitioning (Yuan \& Chesson 2015), which would then cloud our inference on the effect of fluctuation-dependent coexistence.
It is relatively easy to get many species to coexist via the storage effect, but for consistency we constrain our focus to four species communities under the storage effect as well.}

>>>>

The opposing effects of environmental variability on ecosystem variability might explain the mixed results from \new{observational} studies on the diversity-\new{ecosystem variability} relationship.
Observational tests of the diversity-\new{ecosystem variability} relationship, which require sampling across natural diversity gradients, have yielded negative [@Hautier2014], neutral [@Valone2003; @Cusson2015], and positive [@Sasaki2011] relationships.
In a meta-analysis of diversity-\new{ecosystem variability} relationships, @Jiang2009 found no significant evidence for an effect of species richness on ecosystem variability when restricting data to observational studies in terrestrial ecosystems, perhaps because environmental variability varies across natural diversity gradients, affecting both richness and ecosystem variability.
The idiosyncratic results of these observational studies contrast with the consistent conclusions from \new{experimental and theoretical work that ignore, or control, the} feedbacks between variability and richness.

@@

1. Does the diversity-\new{ecosystem} variability relationship remain negative when species coexistence is maintained by the temporal storage effect or relative nonlinearity?

@@

\new{To bound the problem and to isolate the effect of fluctation-dependent coexistence on the diversity-ecosystem stability relationship we constrain our analysis to four species communities and do not consider communities where coexistence is maintained by a combination of mechanisms.
We limit our analysis to four species communities to keep the models tractable while still allowing enough of a species richness gradient for trends to emerge.
It is notoriously difficult to get more than four species to coexist via relative nonlinearity without introducing some form of fluctuation-independent mechanism like resource partitioning} [@Yuan2015], \new{which would then cloud our inference on the effect of fluctuation-dependent coexistence.
It is relatively easy to get many species to coexist via the storage effect, but for consistency we constrain our focus to four species communities under the storage effect as well.}

### 2017-02-23 manuscript/coexistence-stability_ms.tex
trivial writing

The opposing effects of environmental variability on ecosystem
variability might explain the mixed results from \new{observational}
studies on the diversity-\new{ecosystem variability} relationship.
Observational tests of the diversity-\new{ecosystem variability}
relationship, which require sampling across natural diversity gradients,
have yielded negative (Hautier et al. 2014), neutral (Valone \& Hoffman
2003; Cusson et al. 2015), and positive (Sasaki \& Lauenroth 2011)
relationships. In a meta-analysis of
diversity-\new{ecosystem variability} relationships Jiang \& Pu (2009)
found no significant evidence for an effect of species richness on
ecosystem variability when restricting data to observational studies in
terrestrial ecosystems, perhaps because environmental variability varies
across natural diversity gradients, affecting both richness and
ecosystem variability. The idiosyncratic results of these observational
studies contrast with the consistent conclusions from
\new{experimental and theoretical work that ignore, or control, the}
feedbacks between variability and richness.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Does the diversity-variability relationship remain negative when
  species coexistence is maintained by the temporal storage effect or
  relative nonlinearity?
\item
  How does increasing environmental variability impact ecosystem
  variability when coexistence depends on the storage effect or relative
  nonlinearity?
\end{enumerate}

\new{To bound the problem and to isolate the effect of fluctation-dependent coexistence on the diversity-ecosystem stability relationship we constrain our analysis to four species communities and do not consider communities where coexistence is maintained by a combination of mechanisms.
We limit our analysis to four species communities to keep the models tractable while still allowing enough of a species richness gradient for trends to emerge.
It is notoriously difficult to get more than four species to coexist via relative nonlinearity without introducing some form of fluctuation-independent mechanism like resource partitioning (Yuan \& Chesson 2015), which would then cloud our inference on the effect of fluctuation-dependent coexistence.
It is relatively easy to get many species to coexist via the storage effect, but for consistency we constrain our focus to four species communities under the storage effect as well.}

@@

>>>>

The opposing effects of environmental variability on ecosystem
variability might explain the mixed results from \new{observational}
studies on the diversity-\new{ecosystem variability} relationship.
Observational tests of the diversity-\new{ecosystem variability}
relationship, which require sampling across natural diversity gradients,
have yielded negative (Hautier et al. 2014), neutral (Valone \& Hoffman
2003; Cusson et al. 2015), and positive (Sasaki \& Lauenroth 2011)
relationships. In a meta-analysis of
diversity-\new{ecosystem variability} relationships, Jiang \& Pu (2009)
found no significant evidence for an effect of species richness on
ecosystem variability when restricting data to observational studies in
terrestrial ecosystems, perhaps because environmental variability varies
across natural diversity gradients, affecting both richness and
ecosystem variability. The idiosyncratic results of these observational
studies contrast with the consistent conclusions from
\new{experimental and theoretical work that ignore, or control, the}
feedbacks between variability and richness.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Does the diversity-\new{ecosystem} variability relationship remain
  negative when species coexistence is maintained by the temporal
  storage effect or relative nonlinearity?
\item
  How does increasing environmental variability impact ecosystem
  variability when coexistence depends on the storage effect or relative
  nonlinearity?
\end{enumerate}

\new{To bound the problem and to isolate the effect of fluctation-dependent coexistence on the diversity-ecosystem stability relationship we constrain our analysis to four species communities and do not consider communities where coexistence is maintained by a combination of mechanisms.
We limit our analysis to four species communities to keep the models tractable while still allowing enough of a species richness gradient for trends to emerge.
It is notoriously difficult to get more than four species to coexist via relative nonlinearity without introducing some form of fluctuation-independent mechanism like resource partitioning}
(Yuan \& Chesson 2015),
\new{which would then cloud our inference on the effect of fluctuation-dependent coexistence.
It is relatively easy to get many species to coexist via the storage effect, but for consistency we constrain our focus to four species communities under the storage effect as well.}

@@

\hypertarget{ref-Yuan2015}{}
Yuan, C. \& Chesson, P. (2015). The relative importance of relative
nonlinearity and the storage effect in the lottery model.
\emph{Theoretical Population Biology}, 105, 39--52.
